---
title: "A Reproducible Report"
subtitle: "Short-Lecture Zoom: Intro to R & RStudio"
date: 2025-10-07
format:
  html: default
  pdf: default
embed-resources: true
---

This is a Quarto demo script.
You can write text in markdown syntax.

## Import Data

```{r}
#| label: import

penguins <- read.csv("data/penguins.csv")
```

Preview the first lines:

```{r}
#| label: show-head

head(penguins)
```


## Some Stats

```{r}
#| label: summary

summary(penguins)
```


## Visualisation

We will generate a volcano plot to visualize the differential expression analysis results for all included genes.

```{r}
#| label: scatter-plot

library(ggplot2)

ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(alpha = 0.7) +
  facet_grid() +
  theme_light()
```


## Render the Report

Click the Render button and you will get your report!

To learn more about how it works, join the IOC R training program: 
[Registration link](https://docs.google.com/forms/d/e/1FAIpQLSeu9Y8LRxIx1ZKT7yKdzYMduZumRe5Nov4T0JbUPN0f21daQA/viewform?usp=sharing&ouid=107366283096380377724)
